### 2025-09-28 submissions/03-jpam-RR/manuscript_main.tex
Finish section on logistic regression
address R2's comments untill comments 4

\subsection{Measuring Anti-Asian Sentiment}

@@

\subsection*{Dichotomous Asian Racial Identity Reporting and Anti-Asian Bias}

@@

\subsection*{Multinomial Logit Results: Racial Identity Choices and Anti-Asian Bias}

>>>>

\subsection{Measuring Anti-Asian Sentiment}\label{sub:lw-bias}

@@

\subsection*{Dichotomous Asian Racial Identity Reporting and Anti-Asian Bias}\label{sec:results-dichotomous}

@@

\subsection*{Multinomial Logit Results: Racial Identity Choices and Anti-Asian Bias} \label{sec:multinomial}

In this section, I discuss the results from the multinomial logit analysis. These results reveal how anti-Asian bias differentially affects the probability of choosing "Asian only," "White only," or "Asian and White" racial identification, with particularly pronounced effects among mixed-race Asian Americans. Given that the results are mainly driven by individuals with mixed ancestry, I focus the discussion on overall patterns and subsamples with mixed ancestry. The results from the multinomial logit models are in log-odds form, which are difficult to interpret directly. Therefore, I present predicted probabilities and marginal effects to facilitate interpretation.

\subsubsection*{Overall Patterns Among All Generations}

I report main results from estimating equation (\ref{eq:multinomial_logit}) in Figure \ref{fig:pp-all-gen}, showing predicted probabilities from the multinomial logit model, and in Figure \ref{fig:marginal-effects-all}, displaying the corresponding marginal effects.I find that the multinomial logit analysis reveals how anti-Asian bias differentially affects the probability of choosing ``Asian only,'' ``White only,'' or ``Asian and White'' racial identification across all generations. I observe that anti-Asian bias produces the most pronounced effects on racial identity choice. When anti-Asian bias increases from its lowest level (-0.7) to its highest level (1.3), I find that the predicted probability of ``Asian only'' identification decreases dramatically from 98\% to 48\%, representing a 50 percentage point decline. Simultaneously, I observe that ``White only'' identification increases substantially from 1\% to 43\%, while ``Asian and White'' identification shows a modest increase from 1\% to 8\%. The marginal effects confirm these patterns: a one-unit increase in anti-Asian bias decreases the probability of ``Asian only'' identification by approximately 14 percentage points while increasing ``White only'' identification by 11 percentage points.

In contrast, I find that gender and parental education produce minimal effects on racial identity choices across all generations. I observe that female respondents exhibit virtually identical probabilities of ``Asian only'' identification compared to males (91\% vs. 92\%), with minimal variation in ``White only'' (6\% vs. 5\%) and ``Asian and White'' (2\% vs. 3\%) identification. I find that parental education demonstrates similarly limited influence: college-educated fathers show negligible effects, with ``Asian only'' identification remaining stable at 92\% regardless of paternal education status, while ``White only'' and ``Asian and White'' probabilities remain virtually unchanged at 6\% and 2--3\% respectively. I observe that maternal college education produces minimal variation, with ``Asian only'' identification increasing only slightly from 91\% to 92\% when mothers hold college degrees. I find that the marginal effects confirm these modest associations, showing that both gender and parental college education alter ``Asian only'' identification by approximately 1 percentage point. These patterns demonstrate that I find anti-Asian bias drives racial identity choice variation across all generations, while demographic and family characteristics play secondary roles in shaping identity reporting decisions.

\subsubsection*{Second-Generation Subsample by Parental Composition}

I report main results from estimating equation (\ref{eq:multinomial_logit}) for second-generation subsamples by parental composition in Figures \ref{fig:pp-second-aw} and \ref{fig:pp-second-wa}, showing predicted probabilities for AW and WA families respectively. Figure \ref{fig:marginal-effects-second-parental} displays the corresponding marginal effects for both family types. I find that among second-generation Asian Americans, parental composition reveals interesting differences between Asian father-White mother (AW) and White father-Asian mother (WA) families. I observe that anti-Asian bias produces dramatically different effects across these family types. Among AW families, I find that anti-Asian bias effects are particularly pronounced: as bias increases from minimum to maximum levels (-0.7 to 1.3), ``Asian only'' identification probability decreases from 66\% to 28\%, representing a 38 percentage point decline, while ``White only'' identification increases from 3\% to 55\%. Among WA families, I observe even more dramatic patterns: ``Asian only'' identification decreases from 54\% to 18\%, while ``Asian and White'' identification increases from 40\% to 62\%. The marginal effects confirm these patterns: I estimate that a one-unit increase in anti-Asian bias decreases ``Asian only'' identification by approximately 13 percentage points among AW families and 15 percentage points among WA families, while increasing ``White only'' identification by 20 percentage points among AW families and 5 percentage points among WA families.

I find that gender and parental education produce markedly different effects between these family types. Among AW families, I observe that gender has minimal effects: female respondents exhibit virtually identical probabilities of ``Asian only'' identification compared to males (55\% vs. 59\%), with modest increases in ``Asian and White'' identification (32\% vs. 28\%). Among WA families, I find more pronounced gender differences: females show lower ``Asian only'' identification (29\% vs. 26\%) but substantially higher ``Asian and White'' identification (54\% vs. 62\%). When I examine the role of parental education on racial identity choices, I observe that among AW families, having a college-educated father decreases ``Asian only'' identification from 61\% to 53\%, while college-educated mothers increase it from 51\% to 62\%. Among WA families, I find that parental education has minimal effects on racial identity choices, with college-educated fathers and mothers producing virtually no change in identity probabilities across all categories.

I find that the marginal effects reveal how parental education operates differently across AW (Figure \ref{subfig:meaw}) and WA (Figure \ref{subfig:mewa})  family structures, providing insights into the mechanisms through which family composition shapes identity choices. Among AW families, I observe that parental education produces paradoxical effects: having a college-educated father decreases ``Asian only'' identification by approximately 8 percentage points while slightly decreasing ``White only'' identification by 2 percentage points, with the difference flowing toward ``Asian and White'' identification, which increases by 3 percentage points. I find that maternal college education among AW families generates stronger effects in the opposite direction, increasing ``Asian only'' identification by approximately 11 percentage points while decreasing both ``White only'' and ``Asian and White'' identification by 6 and 2 percentage points, respectively.

Among WA families, I observe different patterns where parental education effects are considerably smaller. I find that having a college-educated father produces minimal effects: decreasing ``Asian only'' identification by only 1 percentage point while slightly decreasing ``White only'' identification by 1 percentage point and increasing ``Asian and White'' identification by 4 percentage points. I observe that maternal college education among WA families shows similarly modest effects, increasing ``Asian only'' identification by 3 percentage points while having virtually no effect on ``White only'' identification and decreasing ``Asian and White'' identification by 1 percentage point.

I find that anti-Asian bias effects dwarf parental education influences in both family types. Among AW families, I find that a one-unit increase in anti-Asian bias decreases ``Asian only'' identification by 13 percentage points while dramatically increasing ``White only'' identification by 20 percentage points, with minimal effects on ``Asian and White'' identification. Among WA families, I observe that the same bias increase decreases ``Asian only'' identification by 15 percentage points but increases ``Asian and White'' identification by 8 percentage points and ``White only'' identification by only 5 percentage points. These patterns suggest that I find AW families use White identification as the primary response to bias, while WA families gravitate toward multiracial identification, with parental education serving as a moderating rather than determining factor in these strategic identity choices.

These patterns demonstrate that I find parental composition fundamentally shapes how second-generation Asian Americans respond to social bias, with WA families showing greater preference for multiracial identification and AW families displaying stronger shifts toward White identification under high bias conditions.

\subsection*{Third-Generation Subsample by Grandparent Composition}
I report main results from estimating equation (\ref{eq:multinomial_logit}) for third-generation subsamples by grandparent composition in Figures \ref{fig:pp-third-one}, \ref{fig:pp-third-two}, and \ref{fig:pp-third-three}, with corresponding marginal effects shown in Figure \ref{fig:marginal-effects-third-grandparental}. I find that third-generation Asian Americans demonstrate systematic variation in identity choice patterns based on the number of Asian grandparents, revealing how ancestral dilution affects responsiveness to social bias.

I observe that anti-Asian bias produces dramatically different effects across grandparent combinations. Among those with one Asian grandparent, I find a small response to bias: as bias increases from minimum to maximum levels (-0.7 to 1.3), ``Asian only'' identification decreases modestly from 11\% to 3\%, while ``White only'' identification decreases from 55\% to 49\%, and ``Asian and White'' increases from 34\% to 48\%. Those with two Asian grandparents show intermediate patterns: ``Asian only'' identification decreases from 48\% to 13\%, ``White only'' identification increases from 21\% to 49\%, and ``Asian and White'' identification shifts from 31\% to 38\%. Among those with three Asian grandparents, I find relatively stable effects of bias on racial identity. ``Asian only'' identification remain approximately the same at around 95\% until bias increases from 1 to 1.3 when it decreases by 20 percentage points. The same pattern persists for ``White only'' identification increases from 0\% to 21\% when bias increases from 1 to 1.3, and ``Asian and White'' identification remains constant at 4-6\% regardless of the level of bias.

I find that gender and parental education effects vary systematically across grandparent configurations. Among those with one Asian grandparent, I observe minimal gender effects: females show virtually identical patterns to males across all identity categories (6\% vs. 7\% for ``Asian only,'' 50\% vs. 56\% for ``White only,'' and 44\% vs. 37\% for ``Asian and White''). Those with two Asian grandparents show the most pronounced gender effects: females demonstrate lower ``Asian only'' identification (19\% vs. 22\%) and higher ``White only'' identification (43\% vs. 39\%). Among those with three Asian grandparents, I find modest gender differences: females exhibit slightly lower ``Asian only'' identification (93\% vs. 95\%) and higher ``Asian and White'' identification (7\% vs. 5\%).

I find that parental education operates differently across ancestral configurations. Among those with one Asian grandparent, I observe that paternal college education decreases ``Asian only'' identification from 8\% to 5\% while increasing ``Asian and White'' identification from 38\% to 43\%. Maternal college education shows similar modest effects. Among those with two Asian grandparents, I observe the strongest parental education effects: maternal college education decreases ``Asian only'' identification from 18\% to 23\% while decreasing ``Asian and White'' identification from 45\% to 34\%. Among those with three Asian grandparents, I find that parental education produces stronger effects: paternal college education decreases ``Asian only'' identification from 97\% to 89\% while increasing ``Asian and White'' identification from 3\% to 10\%.

The marginal effects reveal that I find anti-Asian bias produces the strongest effects among those with three Asian grandparents, where a one-unit increase in bias decreases ``Asian only'' identification by approximately 2 percentage points. Among those with one or two Asian grandparents, I observe smaller and often statistically insignificant bias effects. These patterns demonstrate that I find greater Asian ancestry amplifies responsiveness to social bias, while extensive ancestral dilution reduces the salience of anti-Asian attitudes in identity choice decisions.

### 2025-09-28 submissions/03-jpam-RR/manuscript_tab_fig.tex
Finish section on logistic regression
address R2's comments untill comments 4

\begin{center}
\begin{figure}[H]
\caption{Bias and Self-reported Asian Identity in the Least and Most Biased Places}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: All Generations}
\label{fig:pp-all-gen}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for all generations. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means. The analysis includes first-, second-, and third-generation Asian Americans.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: Second Generation Asian Father-White Mother (AW)}
\label{fig:pp-second-aw}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for second-generation Asian Americans with Asian fathers and White mothers. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: Second Generation White Father-Asian Mother (WA)}
\label{fig:pp-second-wa}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for second-generation Asian Americans with White fathers and Asian mothers. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: Third Generation One Asian Grandparent}
\label{fig:pp-third-one}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for third-generation Asian Americans with one Asian grandparent. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: Third Generation Two Asian Grandparents}
\label{fig:pp-third-two}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for third-generation Asian Americans with two Asian grandparents. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: Third Generation Three Asian Grandparents}
\label{fig:pp-third-three}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for third-generation Asian Americans with three Asian grandparents. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

>>>>

\begin{center}
\begin{figure}[H]
\caption{Bias and Self-reported Asian Identity in the Least and Most Biased Places} \label{fig:toptwobias}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (All Generations)}
\label{fig:pp-all-gen}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. The analysis includes first-, second-, and third-generation Asian Americans. First-generation Asian Americans are foreign-born individuals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent. Third-generation Asian Americans are native-born individuals with native-born parents and at least one Asian-born grandparent.}}
\end{figure}
\end{center}

@@

% Marginal Effects: All Generations (after main Multinomial Logit Model plot)
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Marginal Effects of Key Covariates on Racial Identity Choice from Multinomial Logit Model (All Generations)}
\label{fig:marginal-effects-all}
\includegraphics[width=0.9\linewidth]{optimized_marginal_effects_all.png}
\caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using a multinomial logit model. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals. The sample includes first-, second-, and third-generation Asian Americans as defined above.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Second-Generation Asian Americans with Asian Fathers and White Mothers)}
\label{fig:pp-second-aw}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of second-generation Asian Americans with Asian fathers and White mothers. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Second-Generation Asian Americans with White Fathers and Asian Mothers)}
\label{fig:pp-second-wa}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of second-generation Asian Americans with Asian fathers and White mothers. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

% Marginal Effects: Second Generation by Parental Type (AW and WA)
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Marginal Effects of Key Covariates on Racial Identity Choice by Parental Ancestry (Second-Generation Asian Americans)}
\label{fig:marginal-effects-second-parental}

\begin{subfigure}{.48\textwidth}
\caption{Asian Father-White Mother (AW)}\label{subfig:meaw}
\centering
\includegraphics[width=1\linewidth]{optimized_marginal_effects_second_aw.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{White Father-Asian Mother (WA)}\label{subfig:mewa}
\centering
\includegraphics[width=1\linewidth]{optimized_marginal_effects_second_wa.png}
\end{subfigure}

\caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for second-generation Asian Americans by parental ancestry configuration. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Third-Generation Asian Americans with One Asian Grandparent)}
\label{fig:pp-third-one}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with one Asian grandparent. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Third-Generation Asian Americans with Two Asian Grandparents)}
\label{fig:pp-third-two}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with two Asian grandparents. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Third-Generation Asian Americans with Three Asian Grandparents)}
\label{fig:pp-third-three}

@@

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with three Asian grandparents. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means.}}
\end{figure}
\end{center}

@@

% Marginal Effects: Third Generation by Grandparental Type (One, Two, Three Asian Grandparents)
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Marginal Effects of Key Covariates on Racial Identity Choice by Number of Asian Grandparents (Third-Generation Asian Americans)}
\label{fig:marginal-effects-third-grandparental}
\begin{subfigure}{.45\textwidth}
\caption{One Asian Grandparent}\label{subfig:oneasiangrand}
\centering
\includegraphics[width=1\linewidth]{optimized_marginal_effects_third_one.png}
\end{subfigure}
\hfill
\begin{subfigure}{.45\textwidth}
\caption{Two Asian Grandparents}\label{subfig:twoasiangrand}
\centering
\includegraphics[width=1\linewidth]{optimized_marginal_effects_third_two.png}
\end{subfigure}

\begin{subfigure}{.45\textwidth}
\caption{Three Asian Grandparents}\label{subfig:threeasiangrand}
\centering
\includegraphics[width=1\linewidth]{optimized_marginal_effects_third_three.png}
\end{subfigure}
\caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for third-generation Asian Americans by number of Asian grandparents. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals.}}
\end{figure}
\end{center}

### 2025-09-28 submissions/03-jpam-RR/submit_journal.tex
Finish section on logistic regression
address R2's comments untill comments 4

            % The results, presented in Figures \ref{}-\ref{regtab-mnl-third-gen}, reveal that anti-Asian bias significantly decreases the likelihood of reporting ``Asian only'' while increasing the probabilities of both ``White only'' and ``Asian and White/Pacific Islander'' identifications among mixed-ancestry individuals. For example, among second-generation children from Asian father-White mother families, a one standard deviation increase in anti-Asian bias is associated with a 12 percentage point decrease in the probability of reporting ``Asian only,'' a 7 percentage point increase in ``White only,'' and a 5 percentage point increase in ``Asian and White/Pacific Islander.''

@@

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 4. 
        \end{quotation}
        \end{spacing}

>>>>

            I present the results in Figures \ref{fig:pp-all-gen}-\ref{fig:marginal-effects-third-grandparental}, reveal that anti-Asian bias significantly decreases the likelihood of reporting ``Asian only'' while increasing the probabilities of both ``White only'' and ``Asian and White/Pacific Islander'' identifications among mixed-ancestry individuals. For example, among second-generation children from Asian father-White mother families, a one standard deviation increase in anti-Asian bias is associated with a 12 percentage point decrease in the probability of reporting ``Asian only,'' a 20 percentage point increase in ``White only,'' and a 5 percentage points decrease in ``Asian and White/Pacific Islander.'' To discuss these results, I broke down the results into two subsection. The first subsection--- sub-section \ref{sec:results-dichotomous} titles ``Dichotomous Asian Racial Identity Reporting and Anti-Asian Bias''---discusses the dichotomous outcomes. The second subsection---sub-section \ref{sec:multinomial} titled ``Multinomial Logit Results: Racial Identity Choices and Anti-Asian Bias''---focuses on the multinomial outcomes.

@@

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 4. The paper either doesn’t report basic summary statistics about the distribution of bias, or I missed it. The effect of a one-standard-deviation increase in anti-Asian bias on the probability of reporting only Asian appears to be modest.
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}
            \textbf{Response:} I appreciate the reviewer's comments regarding the need for clearer presentation of the bias measures. In the original manuscript, I provided several maps and figures illustrating the geographic distribution of anti-Asian bias across states. In Figure \ref{fig:toptwobias}, I show the aggregate bias index for the two most biased (North Dakota and Tennessee) and two least biased states (Hawaii and Vermont) in Panel \ref{fig:skiniat}. In Panel \ref{fig:Asian-twostates}, I show the self-reported Asian identity rates for the two most biased and two least biased states to illustrate the differences. This would provide visual evidence of the variation in bias levels across states. For example, a one standard deviation bias increases equivalent to moving from Washington, DC, or Vermont to North Dakota in 2020. Additionally, in Figure \ref{fig:skiniat-maps}, I present maps showing the variation in anti-Asian bias across states and over time for my bias index. The maps are of state-level bias in 2004 (Panel \ref{fig:skiniat-map-2004}), 2008 (Panel \ref{fig:skiniat-map-2008}), 2012 (Panel \ref{fig:skiniat-map-2012}), and 2016 (Panel \ref{fig:skiniat-map-2016}). Finally, I show the average state-level bias over the entire sample period in Figure \ref{fig:iat-map-all}. A discussion of these figures is provided in subsection \ref{sub:lw-bias} titled ``Measuring Anti-Asian Sentiment'' in the data section \ref{sec:data}.
    \end{spacing}
